paper_figs_rotations201911 : create paper figures from rotation runs

### 2019-12-02 inst/documents/paper_figs_rotations201911.Rmd
figs

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

ggseq <- ggseq + theme(legend.position="none")
ggrot <- ggrot + theme(legend.position="bottom",
                       axis.title.y = element_blank())

#using patchwork
#plot seq and rot side-by-side
#guides=collect to put legend between plots, doesn't seem to work
(ggseq + ggrot) + plot_layout(guides = 'collect')

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

```{r fig3-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=4, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

# B1 frequency switch insecticides different, no costs no disp

```{r fig4-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r fig1-pcent-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r fig2-which-best-each-gens-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r fig3-which-best-each-gens-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

# Examples of runs where rotations > 20% better than sequences

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=3.5}
#eval false because smaller runs don't have these
#TODO change which runs to show as examples

scenarios_to_plot <- c(624,2167,602,4028,5771)

for(scenario in scenarios_to_plot)
{
  cat(scenario,"\n")

  linputs <- as.list( df_res_all[scenario, 1:15] )

  # run one scenario
  dfres <- do.call(run_rot, linputs)

  rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=TRUE)

  #now run as sequence
  linputs$rot_interval <- 0
  dfres <- do.call(run_rot, linputs)

  rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=TRUE)

  dfi <- data.frame(t(as.data.frame(linputs)))
  names(dfi) <- 'value'
  dfi$inputs <- rownames(dfi)

  #take out columns not between 0 & 1
  dfi <- filter(dfi, !inputs %in% c('max_gen','rot_interval','n_insecticides','plot','min_rwr_interval'))
  #also remove coverage & migration both set to 0 for now
  dfi <- filter(dfi, !inputs %in% c('coverage','migration'))

  ggins <- ggplot(dfi, aes(x=inputs,y=value)) + 
            geom_point() +
            theme_minimal() +
            ylim(0,1) +
            theme(axis.text.x = element_text(angle = 20,hjust = 1, vjust = 1))
  plot(ggins)

@@

```{r figx-PRCC, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

>>>>

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

ggseq <- ggseq + theme(axis.title.x = element_blank()) +
                 ggtitle("A) sequence")
ggrot <- ggrot + theme(legend.position="none")+
                 ggtitle("B) rotation")

#using patchwork
#plot seq and rot side-by-side
#guides=collect to put legend between plots, doesn't seem to work
(ggseq / ggrot) + plot_layout(guides = 'collect')

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

```{r fig3-examp-run-A3, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

@@

# B2 frequency switch insecticides different, costs

```{r fig4-examp-run-B2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#in sequence first insecticide keeps being used for 500 gen
#in rotation switch to other insecticides that reach thereshold means that generations are lost over threshold

dfseq <- run_rot(n_insecticides=3, start_freqs=0.093, cost=c(0.07,0.067,0.032), eff=c(0.8,0.79,0.71),
dom_sel=c(0.23,0.68,0.38), dom_cos=c(0.89,0.65,0.55), rr=c(0.12,0.75,0.33), expo_hi=0.73, male_expo_prop=0.25, coverage=1, migration=0, min_rwr_interval=10)

@@

```{r figx1-pcent-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r figx2-which-best-each-gens-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r figx3-which-best-each-gens-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

@@

```{r figxx-PRCC, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
